Relative parabolic factorizations of Chevalley groups

### 2015-09-03 dennis-vaserstein.tex
Finished rewriting Dennis--Vaserstein combinatorial part

It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.e. ${L_{rs}}^{N_{rs}} \subseteq L_{rs}$. 
Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
It is also clear that $L_{rs}$ contains $\EP_r(R, I)$.

@@

Specializing commutator formula~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
\begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
Clearly, the root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. By~\cref{prop:Stepanov} it is enough to prove the inclusion $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In turn, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show that $\mathcal{X} \subseteq L_{rs}$.

>>>>

It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.e. ${L_{rs}}^{N_{rs}} \subseteq L_{rs}$. 
Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}

@@

Specializing identity~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
\begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
Clearly, the root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In fact, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$.
Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
Indeed, from the identity $t_{0, 1}(-a) = [t_{2,1}(-a); t_{0, 2}(-1)] t_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$
